Reasoning about a Capability Machine with Local Capabilities

### 2017-06-15 popl-2018/paper.tex
store-local -> write-local

However, if we provide the adversary with local capabilities in that first
invocation, then the situation is a bit different. The adversary has no way to
store these local capabilities, so if we make sure that there are also no local
capabilities in the register file for the second invocation (including the
capability being invoked), then the adversary cannot use them any more.%
\footnote{We are ignoring store-local capabilities in this discussion. If the
  adversary does have access to store-local capabilities in the first and second
  invocation, then the memory they address must entirely be cleared before the
  second invocation in order for the reinvocation to remain safe.} Therefore, we
can allow the second invocation to happen in \emph{private} future worlds ($W'
\futurestr W$), in which global safe capabilities remain safe, but local ones
don't. This private future world relation is more liberal than the standard,
public one ($W' \futurewk W$, in which \emph{all} safe capabilities remain
safe). Concretely, worlds may contain \emph{temporary} regions, representing
invariants that only local capabilties may rely on for their safety, and which
may be revoked (disabled) in private future worlds.

Interestingly, this idea is a variant of a notion of public/private future
worlds that has been previously used in the literature (see
Section~\ref{sec:discussion}). However, temporary regions are new in our setting
and there is an interesting interplay with the recursiveness of the worlds: for
a temporary region, the predicate $H \in \Worlds \rightarrow
\powerset{\MemSegments}$ (which defines which memory segments are safe in the
current state of the world) is only required to be monotonous w.r.t.\ public
future worlds (i.e.\ safe memory segments remain safe in public future worlds),
but for permanent regions, it must be monotonous w.r.t.\ private future worlds.
As a consequence, the memory for a permanent region may not contain local
capabilities (as their safety would be broken in private future worlds), which
in turn implies that only local capabilities may have store-local permission (a
general sanity requirement when using local capabilities\footnote{In fact, local
  capabilities become useless as soon as the adversary has access to a single
  global, store-local capability.}).

>>>>

However, if we provide the adversary with local capabilities in that first
invocation, then the situation is a bit different. The adversary has no way to
store these local capabilities, so if we make sure that there are also no local
capabilities in the register file for the second invocation (including the
capability being invoked), then the adversary cannot use them any more.%
\footnote{We are ignoring write-local capabilities in this discussion. If the
  adversary does have access to write-local capabilities in the first and second
  invocation, then the memory they address must entirely be cleared before the
  second invocation in order for the reinvocation to remain safe.} Therefore, we
can allow the second invocation to happen in \emph{private} future worlds ($W'
\futurestr W$), in which global safe capabilities remain safe, but local ones
don't. This private future world relation is more liberal than the standard,
public one ($W' \futurewk W$, in which \emph{all} safe capabilities remain
safe). Concretely, worlds may contain \emph{temporary} regions, representing
invariants that only local capabilties may rely on for their safety, and which
may be revoked (disabled) in private future worlds.

Interestingly, this idea is a variant of a notion of public/private future
worlds that has been previously used in the literature (see
Section~\ref{sec:discussion}). However, temporary regions are new in our setting
and there is an interesting interplay with the recursiveness of the worlds: for
a temporary region, the predicate $H \in \Worlds \rightarrow
\powerset{\MemSegments}$ (which defines which memory segments are safe in the
current state of the world) is only required to be monotonous w.r.t.\ public
future worlds (i.e.\ safe memory segments remain safe in public future worlds),
but for permanent regions, it must be monotonous w.r.t.\ private future worlds.
As a consequence, the memory for a permanent region may not contain local
capabilities (as their safety would be broken in private future worlds), which
in turn implies that only local capabilities may have write-local permission (a
general sanity requirement when using local capabilities\footnote{In fact, local
  capabilities become useless as soon as the adversary has access to a single
  global, write-local capability.}).
